---
title: "group_16_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{group_16_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CentralDogma)
```
## Description
This packages consists of five functions which together generates a random DNA sequence, transcribe it to mRNA, translate it to protein and finally visualize the occurrence of each aminoacid in the sequence. 

## Userguide of each function
The functions can be used as stand alone functions with the correct input. The functions can also be used together to generate DNA sequences and translating them into proteins.

### generate_dna
This function takes the wanted length of the DNA sequence as input, and generate a random DNA sequence with that length as output. 

### mRNA
Takes a DNA sequence as input, change each T to an U, and return the DNA sequence with the changes. 

### make_codons
Takes an mRNA sequence as input, and the start position for translation, default start is 1. The function then split the mRNA sequence into codons of 3 nucleotides, as output. 

### translation
Triplets of 3 nucleotides (codons) are given as input, each codon is translated using the codon table to the correct aminoacid, and the amino acid sequence is returned. 

### visualize_aa_counts
The function takes a protein sequence (amino acid sequence) as input and return a plot showing the counts of each of the aminoacid in the input sequence.







